Scattering of massless particles: scalars, gluons and gravitons

### 2024-07-02 test/main.tex
New

    \begin{alertblock}{Pfaffian}
        Pfaffian is defined for antisymmetric matrix, usually in two ways as following
        \begin{itemize}
            \item \begin{equation*}
                \mathrm{Pf}(A)^2=\det A
            \end{equation*}
            \item \begin{equation*}
                \mathrm{Pf}(A)=\frac{1}{2^n n!}\sum_{\sigma \in S_{2n}}sgn(\sigma)\prod_{i=1}^n a_{\sigma_{(2i-1)},\sigma(2i)}
            \end{equation*}
        \end{itemize}
    \end{alertblock}
\end{frame}
\begin{frame}
    Write down the proposal
    \alert{
    \begin{equation*}
        E_n(\{k,\epsilon,\sigma\})=\mathrm{Pf}^\prime \Psi(k,\epsilon,\sigma)
    \end{equation*}}
\end{frame}

>>>>

    \begin{alertblock}{Pfaffian}
        Pfaffian is defined for antisymmetric matrix, usually in two ways as following
            \item \begin{equation*}
                \mathrm{Pf}(A)^2=\det A
            \item \begin{equation*}
                \mathrm{Pf}(A)=\frac{1}{2^n n!}\sum_{\sigma \in S_{2n}}sgn(\sigma)\prod_{i=1}^n a_{\sigma_{(2i-1)},\sigma(2i)}
    \end{alertblock}
    Write down the proposal
    \alert{
        E_n(\{k,\epsilon,\sigma\})=\mathrm{Pf}^\prime \Psi(k,\epsilon,\sigma)
    \end{equation*}}
    Combine the measure and integrand, we conclude the formula for the tree-level S-matrix of Yang-Mills in any dimension
        M_n^{\mathrm{YM}}(1,2,\dots,n)=\frac{1}{\text{vol SL}(2,\mathbb{C})}\int\frac{d^n\sigma}{\sigma_{12}\cdots\sigma_{n1}}\prod_{a}{}^{\prime}\delta{\left(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\right)}\mathrm{Pf}^{\prime}\Psi
    And using the KLT constrution, we can construct the formula for tree-level S-matrix of gravity as double copy of that of Yang-Mills
        M_n^{\mathrm{gravity}}=\frac{1}{\text{vol SL}(2,\mathbb{C})}\int d^n\sigma\prod_{a}{}^{\prime}\delta{\left(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\right)}\mathrm{Pf}^{\prime}\Psi\mathrm{Pf}^{\prime}\tilde{\Psi}
    We can also write the amplitude in another form
        M_n^{\mathrm{YM}}=\sum_{\{\sigma\}\in\mathrm{solutions}}\frac{1}{\sigma_{12}\cdots\sigma_{n1}}\frac{\mathrm{Pf}^\prime \Psi(k,\epsilon,\sigma)}{\det{'}\Phi}
        M_n^{\mathrm{gravity}}=\sum_{\{\sigma\}\in\mathrm{solutions}}\frac{\det{'}\Psi(k,\epsilon,\sigma)}{\det{'}\Phi}
    where we use the property of Pfaffian $\det{'}\Psi(k,\epsilon,\sigma)=\mathrm{Pf}^\prime \Psi(k,\epsilon,\sigma)$\\$\times \mathrm{Pf}^\prime \Psi(k,\epsilon,\sigma)$.
    \frametitle{Consistency check}
        \item \alert{Gauge invariance}\\
        If we replce the ith polariazation vector $\epsilon_i^\mu$ with momentum $k_i^\mu$, we find that
            C_{ii}=-\sum_{c\neq i}\frac{\epsilon_i\cdot k_c}{\sigma_i-\sigma_c} \to -\sum_{c\neq i}\frac{k_i\cdot k_c}{\sigma_i-\sigma_c}=0
        It is easy to discover that the $i$th and $i+n$th colums become identical, so the determinat and Pfaffian become 0.
        \pause
        \item \alert{Soft limit}
        Using a special property of Pfaffian
            \mathrm{Pf} (E)=\sum_{q=1}^{2n}(-1)^q e_{pq}\mathrm{Pf}(E^{pq}_{pq})
        we find the amplitude in the soft limit is 
            A_n\to\left(\frac{\epsilon_n\cdot k_{n-1}}{k_n\cdot k_{n-1}}+\frac{\epsilon_n\cdot k_1}{k_n\cdot k_1}\right)A_{n-1}
    \frametitle{CHY form of amplitudes}
    Both formulas above can be written in this simplest form 
    \alert{
            \!\!\!\!\mathcal{M}^{(s)}\!=\!\!\!\int\frac{d^n\sigma}{\mathrm{vol\,SL}(2,\mathbb{C})}\prod_a{'}\delta\bigg(\sum_{b\neq a}\frac{s_{ab}}{\sigma_{ab}}\bigg)
            \!\!\!\left(\frac{\mathrm{Tr}(T^{a_1}T^{a_2}\dots T^{a_3})}{(\sigma_1-\sigma_2)\dots (\sigma_n-\sigma_1)}\right)^{(2-s)}{(\mathrm{Pf}^\prime\Psi)}^s
        \end{equation*}}
    with $s=1$ for Yang-Mills and $s=2$ for gravity.
    Here we would like to consider that the formula above is not only a convenient way to write Yang-Mills and gravity amplitudes, but can be \alert{a definition of S-matrix
    for spin s particles}.This means that 
        s=0\quad\to \quad \text{a corresponding sclar theory}
    In order to get more general case, the gravity amplitudes actually can be modified to the product of two different Pfaffians,each with own choice of polariazation vector
        \left(\mathrm{Pf}^\prime \Psi(k,\epsilon,\sigma)\right)^2\to\mathrm{Pf}^\prime \Psi(k,\epsilon,\sigma)\mathrm{Pf}^\prime \Psi(k,\tilde{\epsilon},\sigma)
    actually it gives amplitudes with gravitons coupled to dilatons and B-fields.
    For the case $s=0$, the similar consequence is 
        \left(\frac{\mathrm{Tr}(T^{a_1}T^{a_2}\dots T^{a_n})}{(\sigma_{12})\dots (\sigma_{n1})}\right)^2\to\left(\frac{\mathrm{Tr}(T^{a_1}\dots T^{a_n})}{(\sigma_{12})\dots (\sigma_{n1})}\right)
        \left(\frac{\mathrm{Tr}(\tilde{T}^{b_1}\dots \tilde{T}^{b_n})}{(\sigma_{12})\dots (\sigma_{n1})}\right)
    while the original color group is $U(N)$, the new factors are the product of two different color group \alert{$U(N)\times U(\tilde{N})$}.
    The simplest possibility is the theory with only cubic interaction
        -f_{abc}\tilde{f}_{a^\prime b^\prime c^\prime}\phi^{aa^\prime}\phi^{bb^\prime}\phi^{cc^\prime}
    The conclusion of the factors above
        \mathcal{C}_{U(N)}\equiv \left(\frac{\mathrm{Tr}(T^{a_1}T^{a_2}\dots T^{a_n})}{(\sigma_{12})\dots (\sigma_{n1})}\right)\quad \mathrm{and} \quad E_\epsilon\equiv\mathrm{Pf}^{'}\Psi(\epsilon)
